DATA 621---Business Analytics and Data Mining

### 2020-09-21 HW1/HW1_Group2.Rmd
Unused

```{r eval_set, eval=FALSE}
# Predict target wins
eval_set = eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_SO)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_SO > quantile(TEAM_PITCHING_SO, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr, 
         TEAM_PITCHING_SO < quantile(TEAM_PITCHING_SO, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)

eval_set = eval_set %>% na.omit() %>%
  summarise(iqr = IQR(TEAM_PITCHING_H)) %>%
  bind_cols(eval_set) %>%
  filter(TEAM_PITCHING_H > quantile(TEAM_PITCHING_H, probs = c(0.25), na.rm = TRUE) 
         - 1.5 * iqr,
         TEAM_PITCHING_H < quantile(TEAM_PITCHING_H, probs = c(0.75), na.rm = TRUE) 
         + 1.5 * iqr) %>%
  dplyr::select(-iqr)

eval_set = complete(mice(data = eval_set, method = "pmm", seed = 9450,  print=FALSE), 3)

eval_set = eval_set %>% dplyr::select(-INDEX) %>%
  mutate_if(is.integer, as.numeric) %>%
  mutate(TEAM_BATTING_1B = TEAM_BATTING_H - (TEAM_BATTING_2B + TEAM_BATTING_3B +
                                               TEAM_BATTING_HR))

# Cleaning Test Set for Model #1
test_df1 = eval_set %>%
  mutate(AB = TEAM_BATTING_SO + TEAM_BATTING_BB + TEAM_BATTING_H,
         SLG = (TEAM_BATTING_1B + 2 * TEAM_BATTING_2B + 3 * TEAM_BATTING_3B +
                  4 * TEAM_BATTING_HR) / AB)
# Cleaning Test Set for Model #2
test_df2 = test_df1[, -(17:19)]
test_df2 = data.frame(apply(test_df2, 2, scale))
# Cleaning Test Set for Model #3
test_df3 = cbind(test_df1, sapply(test_df1[1:length(test_df1)], function(x) x^2))
names(test_df3) = make.unique(names(test_df3), sep = "_")
```

@@

# CODE APPENDIX
The code chunks below represent the R code called in order during the analysis.
They are reproduced in the appendix for review and comment.
```{r appendix, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r setup}
```
```{r loadData}
```
```{r wins}
```
```{r pctNull}
```
```{r negFactors}
```
```{r posFactors}
```
```{r summaryInfo}
```
```{r fewOutliers}
```
```{r manyOutliers}
```
```{r otherOutliers}
```
```{r corrPlot}
```
```{r outliers_1}
```
```{r iqr_removal_SO}
```
```{r iqr_removal_H}
```
```{r outlier_boxplot}
```
```{r impute_train}
```
```{r singles}
```
```{r make_slg_obp}
```
```{r slugging_compare}
```
```{r baseModel}
```
```{r cooks_distance}
```
```{r model2C+S}
```
```{r model2}
```
```{r model3}
```
```{r performance}
```
<!--```{r eval_set}
```-->
```{r predictions}
```

>>>>

@@

# CODE APPENDIX
The code chunks below represent the R code called in order during the analysis.
They are reproduced in the appendix for review and comment.
```{r appendix, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r setup}
```
```{r loadData}
```
```{r wins}
```
```{r pctNull}
```
```{r negFactors}
```
```{r posFactors}
```
```{r summaryInfo}
```
```{r fewOutliers}
```
```{r manyOutliers}
```
```{r otherOutliers}
```
```{r corrPlot}
```
```{r outliers_1}
```
```{r iqr_removal_SO}
```
```{r iqr_removal_H}
```
```{r outlier_boxplot}
```
```{r impute_train}
```
```{r singles}
```
```{r make_slg_obp}
```
```{r slugging_compare}
```
```{r baseModel}
```
```{r cooks_distance}
```
```{r model2C+S}
```
```{r model2}
```
```{r model3}
```
```{r performance}
```
```{r predictions}
```
